Open Source, Collaborative Curriculum

### 2017-04-27 siip.tex
external outcomes

          \paragraph{Student Outcomes}
          Students enrolled in NPRE412 at UIUC and peer courses at partner 
          institutions (USC, UT-Knoxville, Kansas State University, and 
          UW-Madison) will have an improved experience. Their 
          curriculum will be bolstered by the comprehensive concept mapping 
          process as well as exercises and assessment tools reviewed by and 
          improved by the expertise of professors at peer institutions.

@@

@@

          \section*{Budget Justification}
          Explain travel for external collaborators, meals, meeting space, etc. 
          Host it in the Union?

>>>>

          \paragraph{Student Outcomes}
          Students enrolled in NPRE412 at UIUC and peer courses at partner 
          institutions (USC, UT-Knoxville, Kansas State University, and 
          UW-Madison) will have an improved experience. Their 
          curriculum will be bolstered by the comprehensive concept maps 
          underlying their coursework\cite{concept_maps}, as well as exercises 
          and assessment tools reviewed and improved by expert professors at 
          peer institutions.

@@

          \paragraph{External Outcomes}

          Of perhaps most relevance in the context of this work is the 
          potential impact externally. This effort should spawn an 
          instruction-centric community of 
          practice among colleagues previously primarily connected by research 
          in their specific technical subdomain.

@@

          \section*{Budget Justification}
          The two workshops will 
          Explain travel for external collaborators, meals, meeting space, etc. 
          Host it in the Union?
